tikz

### 2023-10-09 Analysis/e3_test.qmd
update E2 and E3 results, and re-render

@@

result <- test_summary_table(testE3, "dist", mfun = list(mean = mean, median = median, sd = sd))
result$constant
result$varied

@@

```{r}
#| label: fig-e3-test-dev
#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  labs(x="Band", y="Deviation From Target")
```

@@

modelName <- "e3_testDistBand_RF_5K"
e3_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=testE3,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)
mp3 <- GetModelStats(e3_distBMM) |> kable(escape=F,booktabs=T)
mp3
```

In experiment 3, the overall effect of training condition shows a similar pattern to that of Experiment 2, with a  moderately strong effect tendency for the varied group to show lower deviation (β = -91.09, 95% CI [-182.79, 3.75]), with 97% of the posterior distribution falling under 0. (NEED TO CONTROL FOR BAND ORDER HERE)

@@

```{r}
#| label: fig-e3-ame
#| fig-cap: e3. Predicted Means Per Condition and Band, and Average Marginal Effect (Constant - Varied)
#| fig-width: 10
#| fig-height: 10
new_data_grid=map_dfr(1, ~data.frame(unique(testE3[,c("id","condit","bandInt")])))

cSamp <- e3_distBMM |> 
  emmeans("condit",by="bandInt",at=list(bandInt=c(100,350,600,800,1000,1200)),
          epred = TRUE, re_formula = NA) |> 
  pairs() |> gather_emmeans_draws()  |>
  group_by(contrast, .draw,bandInt) |> summarise(value=mean(.value), n=n())

 ameBand <- cSamp |> ggplot(aes(x=value,y="")) + 
  stat_halfeye() + 
  geom_vline(xintercept=0,alpha=.4)+
  facet_wrap(~bandInt,ncol=1) + labs(x="Marginal Effect (Constant - Varied)", y= NULL)+
  ggtitle("Average Marginal Effect")

bothConditGM <- e3_distBMM %>%
  epred_draws(newdata = new_data_grid,ndraws = 2000, re_formula = NA) |>
  ggplot(aes(x=.epred,y="Mean",fill=condit)) + 
  stat_halfeye() +facet_wrap(~bandInt, ncol = 1) +
  labs(x="Predicted Deviation", y=NULL)+
  ggtitle("Grand Means") +theme(legend.position = "bottom")

(bothConditGM | ameBand) + plot_layout(widths=c(2,1.0))
```

@@

```{r}
#| label: fig-e3-test-vx
#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9
testE3 %>% group_by(id,vb,condit) |> plot_distByCondit()

@@

result <- test_summary_table(testE3, "vx", mfun = list(mean = mean, median = median, sd = sd))
result$constant 
result$varied

```{r}
#| label: tbl-e3-bmm-vx
#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
mt4 <-GetModelStats(e3_vxBMM ) |> kable(escape=F,booktabs=T)
mt4
```

See @tbl-e3-bmm-vx for the full model results. The estimated coefficient for training condition (β = -166.75, 95% CI [-277.14, -64.08]) suggests that the varied group tends to produce softer throws than the constant group. More relevant to the issue of discrimination is the slope on Velocity Band (β = 0.44, 95% CI [.35, .52]). Although the median slope does fall underneath the ideal of value of 1, the fact that the 95% credible interval does not contain 0 provides strong evidence that participants exhibted some discrimination between bands. It's also noteworthy that the difference between the E3 slope and E1 & E2 slope is quite strong, with the upper end of the 95% CI for E3 falling underneath the lower end of the 95% CI for both of the earlier experiments.

@@

```{r}
#| label: fig-e3-slope-dist
#| fig-cap: Slope estimates by participant - ordered from lowest to highest within each condition. 
#| fig-height: 9
#| fig-width: 10

@@

indv_coefs <- coef(e3_vxBMM)$id |> 
  as_tibble(rownames="id") |> 
  select(id, starts_with("Est")) |>
  left_join(e3Sbjs, by=join_by(id) ) |> 
  group_by(condit) |> 
  mutate(rank = rank(desc(Estimate.bandInt)),
         intErrorRank=rank((Est.Error.Intercept)),
         bandErrorRank=rank((Est.Error.bandInt)),
         nCond = n()) |> arrange(intErrorRank)

@@

random_effects <- e3_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 2000) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(testE3$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

cd <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  mutate(Slope=bandInt_RF+b_bandInt) |> group_by(id)

cdMed <- cd |> group_by(id) |> median_qi(Slope)  |> 
  left_join(e3Sbjs, by=join_by(id)) |> group_by(condit) |>
  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)

cdMed %>% ggplot(aes(y=rankSlope, x=Slope,fill=condit,color=condit)) + 
  geom_pointrange(aes(xmin=.lower , xmax=.upper)) + 
  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit)

# cdMed |>  ggplot(aes(x = condit, y = Slope,fill=condit)) +
#     stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
#     stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
#   geom_jitter()
#   labs(x="Band", y="Deviation From Target")

@@

```{r}
#| label: fig-e3-indv-slopes
#| fig-cap: Subset of Varied and Constant Participants with the largest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-height: 11

nTop <- 2

combined_df <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt) |>
  right_join(new_data_grid, by = join_by("id"),relationship="many-to-many") |> 
  mutate(
    fixed_effects = b_Intercept +
      (bandInt * b_bandInt) +
      condit_dummy * b_conditVaried + 
      (bandInt * condit_dummy) * `b_conditVaried:bandInt` ,  # Note: Replace : with correct operator
    random_effects = Intercept + bandInt_RF,  # Assuming random effects for intercept and bandInt
    estimate = fixed_effects + random_effects
  )

combined_df |> 
  filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id)) )  |> 
  group_by(id, bandInt) |>
  sample_n(200) |>
  ggplot(aes(x=bandInt,y=estimate)) + 
  geom_abline(aes(intercept=Intercept+b_Intercept, slope=bandInt_RF+b_bandInt), color="grey50", alpha=.1) +
  geom_abline(data=indv_coefs |> 
                filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id))),aes(intercept=Estimate.Intercept,slope=Estimate.bandInt),color="red") +
  stat_pointinterval(data=testE3 |> filter(id %in% (indv_coefs |> filter(rank<=nTop) |> pull(id))), aes(x=bandInt,y=vx, color=vb)) +
  facet_nested_wrap(vars(condit,id),ncol = 2) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE3$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +  ylab("X Velocity") + xlab("Band")

@@

```{r}
#| label: fig-e3-indv-slopes-small
#| fig-cap: Subset of Varied and Constant Participants with the smallest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-height: 11

nTop <- 2

combined_df |> 
  filter(id %in% (indv_coefs |> filter(rank>nCond-nTop) |> pull(id)) )  |> 
  group_by(id, bandInt) |>
  sample_n(200) |>
  ggplot(aes(x=bandInt,y=estimate)) + 
  geom_abline(aes(intercept=Intercept+b_Intercept, slope=bandInt_RF+b_bandInt), color="grey50", alpha=.1) +
  geom_abline(data=indv_coefs |> 
                filter(id %in% (indv_coefs |> filter(rank>nCond-nTop) |> pull(id))),aes(intercept=Estimate.Intercept,slope=Estimate.bandInt),color="red") +
  stat_pointinterval(data=testE3 |> filter(id %in% (indv_coefs |> filter(rank>nCond-nTop) |> pull(id))), aes(x=bandInt,y=vx, color=vb)) +
  facet_nested_wrap(vars(condit,id),ncol = 2) +
  scale_x_continuous(breaks = c(100, 350, 600, 800, 1000, 1200), 
                     labels = levels(testE3$vb), 
                     limits = c(0, 1400)) +
  theme(axis.text.x = element_text(angle = 45, hjust = 0.5, vjust = 0.5)) +  ylab("X Velocity") + xlab("Band")

>>>>

adlkdj

@@

resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
resultOrig$constant 
resultOrig$varied

resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "dist","Deviation", mfun = list(mean = mean, median = median, sd = sd))
resultRev$constant 
resultRev$varied

@@

```{r}
#| label: fig-e3-test-dev
#| fig-cap: e3. Deviations from target band during testing without feedback stage. 
testE3 |>  ggplot(aes(x = vb, y = dist,fill=condit)) +
    stat_summary(geom = "bar", position=position_dodge(), fun = mean) +
    stat_summary(geom = "errorbar", position=position_dodge(.9), fun.data = mean_se, width = .4, alpha = .7) + 
  labs(x="Band", y="Deviation From Target") + facet_wrap(~bandOrder)
```

@@

modelName <- "e3_testDistBand_RF_5K"
e3_distBMM <- brm(dist ~ condit * bandInt + (1 + bandInt|id),
                      data=testE3,file=paste0(here::here("data/model_cache",modelName)),
                      iter=5000,chains=4)
mp3 <- GetModelStats(e3_distBMM) |> kable(escape=F,booktabs=T)
mp3

cd1 <- get_coef_details(e3_distBMM, "conditVaried")
sc1 <- get_coef_details(e3_distBMM, "bandInt")
intCoef1 <- get_coef_details(e3_distBMM, "conditVaried:bandInt")
```

In experiment 3, the overall effect of training condition shows a similar pattern to that of Experiment 2, with a  moderately strong effect tendency for the varied group to show lower deviation (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]), with 97% of the posterior distribution falling under 0. (NEED TO CONTROL FOR BAND ORDER HERE)

@@

@@

```{r}
#| label: fig-e3-test-vx
#| fig-cap: e3 testing x velocities. Translucent bands with dash lines indicate the correct range for each velocity band. 
#| fig-width: 11
#| fig-height: 9
# testE3 |> filter(bandOrder=="Original")|> group_by(id,vb,condit) |> plot_distByCondit()
# testE3 |> filter(bandOrder=="Reverse")|> group_by(id,vb,condit) |> plot_distByCondit() +ggtitle("test")

testE3 |> group_by(id,vb,condit,bandOrder) |> plot_distByCondit() + facet_wrap(bandOrder~condit,scale="free_x")

@@

resultOrig <- test_summary_table(testE3 |> filter(bandOrder=="Original"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
resultOrig$constant 
resultOrig$varied

resultRev <- test_summary_table(testE3 |> filter(bandOrder=="Reverse"), "vx","X Velocity", mfun = list(mean = mean, median = median, sd = sd))
resultRev$constant 
resultRev$varied 
```

```{r}
#| label: tbl-e3-bmm-vx
#| tbl-cap: "Experiment 3. Bayesian Mixed Model Predicting Vx as a function of condition (Constant vs. Varied) and Velocity Band"
e3_vxBMM <- brm(vx ~ condit * bandInt + (1 + bandInt|id),
                        data=testE3,file=paste0(here::here("data/model_cache", "e3_testVxBand_RF_5k")),
                        iter=5000,chains=4,silent=0,
                        control=list(adapt_delta=0.94, max_treedepth=13))
mt4 <-GetModelStats(e3_vxBMM ) |> kable(escape=F,booktabs=T)
mt4

cd1 <- get_coef_details(e3_vxBMM, "conditVaried")
sc1 <- get_coef_details(e3_vxBMM, "bandInt")
intCoef1 <- get_coef_details(e3_vxBMM, "conditVaried:bandInt")
```

See @tbl-e3-bmm-vx for the full model results. The estimated coefficient for training condition (β = `r cd1$estimate`, 95% CrI \[`r cd1$conf.low`, `r cd1$conf.high`\]) suggests that the varied group tends to produce softer throws than the constant group. More relevant to the issue of discrimination is the slope on Velocity Band (β = `r sc1$estimate`, 95% CrI \[`r sc1$conf.low`, `r sc1$conf.high`\]).
Interaction: (β = `r intCoef1$estimate`, 95% CrI \[`r intCoef1$conf.low`, `r intCoef1$conf.high`\])

It's also noteworthy that the difference between the E3 slope and E1 & E2 slope is quite strong, with the upper end of the 95% CI for E3 falling underneath the lower end of the 95% CI for both of the earlier experiments.

@@

```{r}
#| label: tbl-e3-slope-quartile
#| tbl-cap: "Slope coefficients by quartile, per condition"

@@

indv_coefs <- as_tibble(coef(e3_vxBMM)$id, rownames="id")|> 
  select(id, starts_with("Est")) |>
  left_join(e3Sbjs, by=join_by(id) )

@@

random_effects <- e3_vxBMM |> 
  gather_draws(`^r_id.*$`, regex = TRUE, ndraws = 1500) |> 
  separate(.variable, into = c("effect", "id", "term"), sep = "\\[|,|\\]") |> 
  mutate(id = factor(id,levels=levels(testE3$id))) |> 
  pivot_wider(names_from = term, values_from = .value) |> arrange(id,.chain,.draw,.iteration)

 indvDraws <- left_join(random_effects, fixed_effects, by = join_by(".chain", ".iteration", ".draw")) |> 
  rename(bandInt_RF = bandInt,RF_Intercept=Intercept) |>
  right_join(new_data_grid, by = join_by("id")) |> 
  mutate(
    Slope = bandInt_RF+b_bandInt,
    Intercept= RF_Intercept + b_Intercept,
    estimate = (b_Intercept + RF_Intercept) + (bandInt*(b_bandInt+bandInt_RF)) + (bandInt * condit_dummy) * `b_conditVaried:bandInt`,
    SlopeInt = Slope + (`b_conditVaried:bandInt`*condit_dummy)
  )

  indvSlopes <- indvDraws |> group_by(id) |> median_qi(Slope,SlopeInt, Intercept,b_Intercept,b_bandInt) |>
  left_join(e3Sbjs, by=join_by(id)) |> group_by(condit) |>
    select(id,condit,Intercept,b_Intercept,starts_with("Slope"),b_bandInt, n) |>
  mutate(rankSlope=rank(Slope)) |> arrange(rankSlope)   |> ungroup()

  indvSlopes |> mutate(Condition=condit) |>  group_by(Condition) |> 
    reframe(enframe(quantile(SlopeInt, c(0.0,0.25, 0.5, 0.75,1)), "quantile", "SlopeInt")) |> 
  pivot_wider(names_from=quantile,values_from=SlopeInt,names_prefix="Q_") |>
  group_by(Condition) |>
  summarise(across(starts_with("Q"), list(mean = mean))) |> kbl()

@@

@fig-e3-bmm-bx2 shows the distributions of estimated slopes relating velocity band to x velocity for each participant, ordered from lowest to highest within condition. Slope values are lower overall for varied training compared to constant training. Figure Xb plots the density of these slopes for each condition. The distribution for varied training has more mass at lower values than the constant training distribution. Both figures illustrate the model's estimate that varied training resulted in less discrimination between velocity bands, evidenced by lower slopes on average.

```{r}
#| label: fig-e3-bmm-bx2
#| fig-cap: Slope distributions between condition
#| fig-subcap: ["Slope estimates by participant - ordered from lowest to highest within each condition. ", "Destiny of slope coefficients by training group"]
#| fig-height: 11
#| fig-width: 12

indvSlopes |> ggplot(aes(y=rankSlope, x=SlopeInt,fill=condit,color=condit)) + 
  geom_pointrange(aes(xmin=SlopeInt.lower , xmax=SlopeInt.upper)) + 
  labs(x="Estimated Slope", y="Participant")  + facet_wrap(~condit) +
ggplot(indvSlopes, aes(x = SlopeInt, color = condit)) + 
geom_density() + labs(x="Slope Coefficient",y="Density")

@@

```{r}
#| label: fig-e3-indv-slopes
#| fig-cap: Subset of Varied and Constant Participants with the smallest and largest estimated slope values. Red lines represent the best fitting line for each participant, gray lines are 200 random samples from the posterior distribution. Colored points and intervals at each band represent the empirical median and 95% HDI. 
#| fig-subcap: ["subset with largest slopes", "subset with smallest slopes"]
#| fig-height: 11
#| fig-width: 12
nSbj <- 3
indvDraws  |> indv_model_plot(indvSlopes, testE3Avg, SlopeInt,rank_variable=Slope,n_sbj=nSbj,"max")
indvDraws |> indv_model_plot(indvSlopes, testE3Avg,SlopeInt, rank_variable=Slope,n_sbj=nSbj,"min")

### 2023-10-09 Analysis/methods.qmd
update E2 and E3 results, and re-render

```{dot}
//| label: fig-design-e1
//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
//| fig-width: 8.0
//| fig-height: 2.5
//| fig-responsive: false
digraph {
  graph [layout = dot, rankdir = LR]

>>>>

```{dot}
//| label: fig-design-e1
//| fig-cap: "Experiment 1 Design. Constant and Varied participants complete different training conditions."
//| fig-width: 8.0
//| fig-height: 2.5
//| fig-responsive: false
//| column: screen-inset-right
digraph {
  graph [layout = dot, rankdir = LR]

### 2023-10-09 Misc/Visuals_Interactives/tikz_net.qmd
update E2 and E3 results, and re-render

>>>>

\

## Alcove

```{r, engine = 'tikz'}

\begin{tikzpicture}[node distance=1cm]
    \tikzset{
        neuron/.style={
            circle,
            draw,
            minimum size=1cm,
        },
        input neuron/.style={
            neuron,
            fill=green!20,
        },
        output neuron/.style={
            neuron,
            fill=red!20,
        },
        hidden neuron/.style={
            neuron,
            fill=blue!20,
        },
    }

    \node[input neuron] (input-1) at (0, 0) {Stimulus dimension node 1};
    \node[input neuron] (input-2) [below=of input-1] {Stimulus dimension node 2};
    \node[hidden neuron] (hidden-1) [right=of input-1] {Exemplar node 1};
    \node[hidden neuron] (hidden-2) [below=of hidden-1] {Exemplar node 2};
    \node[hidden neuron] (hidden-3) [below=of hidden-2] {Exemplar node 3};
    \node[output neuron] (output-1) [right=of hidden-2] {Category node 1};
    \node[output neuron] (output-2) [right=of hidden-3] {Category node 2};

    \draw[->] (input-1) -- (hidden-1);
    \draw[->] (input-1) -- (hidden-2);
    \draw[->] (input-1) -- (hidden-3);
    \draw[->] (input-2) -- (hidden-1);
    \draw[->] (input-2) -- (hidden-2);
    \draw[->] (input-2) -- (hidden-3);
    \draw[->] (hidden-1) -- node[midway, above, sloped]{Learned association weights} (output-1);
    \draw[->] (hidden-2) -- node[midway, above, sloped]{Learned association weights} (output-1);
    \draw[->] (hidden-3) -- node[midway, above, sloped]{Learned association weights} (output-2);
\end{tikzpicture}

### Alcove 2
```{r, engine = 'tikz'}
#| eval: true
#| cache: true

\tikzset{
    neuron/.style={
        circle,
        draw,
        minimum size=1cm,
    },
    input neuron/.style={
        neuron,
        fill=green!20,
    },
    output neuron/.style={
        neuron,
        fill=red!20,
    },
    hidden neuron/.style={
        neuron,
        fill=blue!20,
    },
}

\begin{tikzpicture}[node distance=1cm]
    \node[input neuron] (input-1) at (0, 0) {Stimulus dimension node 1};
    \node[input neuron] (input-2) [below=of input-1] {Stimulus dimension node 2};
    \node[hidden neuron] (hidden-1) [right=of input-1] {Exemplar node 1};
    \node[hidden neuron] (hidden-2) [below=of hidden-1] {Exemplar node 2};
    \node[hidden neuron] (hidden-3) [below=of hidden-2] {Exemplar node 3};
    \node[output neuron] (output-1) [right=of hidden-2] {Category node 1};
    \node[output neuron] (output-2) [right=of hidden-3] {Category node 2};

    \draw[->] (input-1) -- (hidden-1);
    \draw[->] (input-1) -- (hidden-2);
    \draw[->] (input-1) -- (hidden-3);
    \draw[->] (input-2) -- (hidden-1);
    \draw[->] (input-2) -- (hidden-2);
    \draw[->] (input-2) -- (hidden-3);
    \draw[->] (hidden-1) -- node[midway, above, sloped]{Learned association weights} (output-1);
    \draw[->] (hidden-2) -- node[midway, above, sloped]{Learned association weights} (output-1);
    \draw[->] (hidden-3) -- node[midway, above, sloped]{Learned association weights} (output-2);
\end{tikzpicture}
```
